Assessing the Impact of Financial Assistances on Business and Income Outcomes: A Gender-Specific Analysis

### 2024-02-15 paper/paper.qmd
paper.qmd

In the wake of global economic downturns, microenterprise development has gained attention for its critical role in bolstering grassroots economic resilience and empowerment. This sector's growth is influenced not only by the type of financial support it receives—commonly categorized as loans, cash grants, or in-kind grants—but also by the personal attributes of the enterprise owners. Earlier research, such as that by Field et al., has highlighted the potential of flexible microcredit arrangements to spur company growth (Field et al., 2013), while Banerjee et al. have underscored personal characteristics like experience or optimism as key determinants of capital returns (Banerjee et al., 2019). Nonetheless, debate persists regarding the most effective form of financial support for microenterprises. Taking a step further, the seminal study "Is It Who You Are or What You Get? Comparing the Impacts of Loans and Grants for Microenterprise Development" by Crépon, El Komi, and Osman, provided a randomized examination of 3294 entrepreneurs to assess the relative importance of financial support type versus owner characteristics in enterprise performance (Crépon et al., 2024). They reported that individual differences among owners could have more influence than the type of financial support received. Their work also suggested that, while all forms of support enhanced enterprise assets and profits, in-kind grants were particularly effective. However, it doesn’t justify any of the approaches to be the most effective, as there are many factors other than controlled variable, including ages and genders (Crépon et al., 2024). Therefore, this report only proves the existence of a correlation between the type of financial support and the business outcomes, but not a causal relationship. In our study, we utilized randomization on their experiment dataset to minimize the impact of irrelevant variables, enabling us to investigate which form of support yields the most significant impact on business outcomes.

@@

The original research paper used Stata (StataCorp 2021) for data processing and analysis within its replication package. However, we opted for R (R Core Team 2020) to conduct all data organization and analysis, employing R packages such as tidyverse (Wickham et al. 2019) for data manipulation, ggthemes (Arnold 2021) and ggprism (Dawson 2021) for creating figures, and patchwork (Pedersen 2020) for arranging them. Additionally, we used kableExtra (Zhu 2021) to generate tables and havehave (Wickham, Miller, and Smith 2022) for reading dta files.

@@

Our data cleaning and processing workflow was designed to ensure that the dataset was robust and suitable for the statistical analysis required to answer our research questions. The R programming language (R Core Team 2020), along with a suite of packages including `haven`, `dplyr`, `readr`, `ggplot2`, `knitr`, `kableExtra`, and `stargazer`, was utilized for data manipulation and analysis.
We began by loading the dataset from two Stata files using the `haven` package. The pre-intervention (`pre_data`) and post-intervention (`out_data`) data were both read and filtered to include only the entries that were present in both datasets, ensuring consistency and completeness for each subject across the study timeline.
A new dataset (`new_data`) was created to store the cleaned variables. We treated the `treatment_status` variable by creating dummy variables for each type of financial support, which were then bound to `new_data`. 
We defined several key outcome variables to assess the impact of the financial interventions:

>>>>

In the wake of global economic downturns, microenterprise development has gained attention for its critical role in bolstering grassroots economic resilience and empowerment. This sector's growth is influenced not only by the type of financial support it receives—commonly categorized as loans, cash grants, or in-kind grants—but also by the personal attributes of the enterprise owners. Earlier research, such as that by Field et al., has highlighted the potential of flexible microcredit arrangements to spur company growth [@field2013does], while Banerjee et al. have underscored personal characteristics like experience or optimism as key determinants of capital returns [@banerjee2019universal]. Nonetheless, debate persists regarding the most effective form of financial support for microenterprises. Taking a step further, the seminal study "Is It Who You Are or What You Get? Comparing the Impacts of Loans and Grants for Microenterprise Development" by Crépon, El Komi, and Osman, provided a randomized examination of 3294 entrepreneurs to assess the relative importance of financial support type versus owner characteristics in enterprise performance [@crepon2024you]. They reported that individual differences among owners could have more influence than the type of financial support received. Their work also suggested that, while all forms of support enhanced enterprise assets and profits, in-kind grants were particularly effective. However, it doesn’t justify any of the approaches to be the most effective, as there are many factors other than controlled variable, including ages and genders [@crepon2024you]. Therefore, this report only proves the existence of a correlation between the type of financial support and the business outcomes, but not a causal relationship. In our study, we utilized randomization on their experiment dataset to minimize the impact of irrelevant variables, enabling us to investigate which form of support yields the most significant impact on business outcomes.

@@

The original research paper used Stata for data processing and analysis within its replication package. However, we opted for R [@citeR] to conduct all data organization and analysis. We used a suite of R libraries including `haven` [@haven] for reading Stata files, `readr` [@citereadr] for data import, `ggplot2` [@citeggplot2] for data visualization, `dplyr` [@citedplyr] for data manipulation, `knitr` [@citeknitr] for report generation, `kableExtra` [@citekableExtra] for table formatting, and `stargazer` [@stargazer] for creating regression tables. These libraries were selected for their functionality and compatibility with our dataset and analysis requirements.

@@

Our data cleaning and processing workflow was designed to ensure that the dataset was robust and suitable for the statistical analysis required to answer our research questions. The R programming language [@citeR], along with a suite of packages including `haven` [@haven], `dplyr` [@citedplyr], `readr` [@citereadr], `ggplot2` [@citeggplot2], `knitr` [@citeknitr], `kableExtra` [@citekableExtra], and `stargazer` [@stargazer], was utilized for data manipulation and analysis.

We began by loading the dataset from two Stata files using the `haven` package. The pre-intervention (`pre_data`) and post-intervention (`out_data`) data were both read and filtered to include only the entries that were present in both datasets, ensuring consistency and completeness for each subject across the study timeline.
A new dataset (`new_data`) was created to store the cleaned variables. We treated the `treatment_status` variable by creating dummy variables for each type of financial support, which were then bound to `new_data`. 
We defined several key outcome variables to assess the impact of the financial interventions:
